---
title: "HW2"
author: "Olivia Chen"
date: "February 2, 2016"
output: pdf_document
---



```{r}
library(ISLR)
summary(Weekly)
pairs(Weekly)
```

**(a)From 1089 weekly returns from 1990 to 2010, the frequency that the market is up is 605, and 484 is frequency for market downtime. There's something very interesting in the pairs plot, which is that there's obvious relationship between year and volumn.**

```{r}
attach(Weekly)
logis = glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, 
    family = binomial)
summary(logis)
```

**(b)Looking at the summary of the logistic regreesion, it seems like lag2 is the only predictor that is significant with p value is 0.02. **

```{r}
glm.probs=predict(logis,type="response")
contrasts(Direction)
glm.probs[1:10]
glm.pred=rep("Down",1089)
glm.pred[glm.probs>.5]="Up"
```

**This is the confusion matrix**
```{r}
table(glm.pred,Direction)
print(paste0("The overall fraction of correct predictions is:",round(mean(glm.pred==Direction),2)))
```

**(c)We can see that this logistic regression does better job when prediting up, because the chance that it predicts a down direction corretly is only 54/494 =  11%, However, the chance that it predicts a up direction corretly is 557/605 = 92%.**

```{r}
train = (Year < 2009)
Weekly.0910 = Weekly[!train, ]
glm.fit = glm(Direction ~ Lag2, data = Weekly, family = binomial, subset = train)
glm.probs = predict(glm.fit, Weekly.0910, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
Direction.0910 = Direction[!train]
table(glm.pred, Direction.0910)
print(paste0("The overall fraction of correct predictions is:",round(mean(glm.pred==Direction.0910),2)))
```


