---
title: "Lab 3"
author: "Olivia Chen"
date: "February 10, 2016"
output: pdf_document
Professor: Prof. Maslova
Class: Data Analysis
---



```{r, echo=FALSE}
library(ISLR)
summary(Default)
attach(Default)
dim(Default)
```

**a. We can see that this dataframe has 10000 rows and 4 varivales, and that's the summary of the data set**

```{r, echo=FALSE, eval=FALSE, warning=FALSE}
#i.
glm.fit = glm(default ~ income + balance, data = Default, family = binomial)
#ii
set.seed(10)
train=sample(10000,8000)
glm.fit = glm(default ~ income + balance, data = Default, family = binomial, 
        subset = train)
#iii
glm.probs = predict(glm.fit, Default[-train, ], type = "response")
glm.pred = rep("No", 2000)
glm.pred[glm.probs > 0.5] = "Yes"
#iv
mean(glm.pred != Default[-train, ]$default)
```

**b. I splited the data into 80% training data and 20% validation data. The validation set error I got is 0.0315**


```{r, echo=FALSE, eval=FALSE, warning=FALSE}

#ii
set.seed(20)
train=sample(10000,8000)
glm.fit = glm(default ~ income + balance, data = Default, family = binomial, 
        subset = train)
#iii
glm.probs = predict(glm.fit, Default[-train, ], type = "response")
glm.pred = rep("No", 2000)
glm.pred[glm.probs > 0.5] = "Yes"
#iv
mean(glm.pred != Default[-train, ]$default)
set.seed(40)
train=sample(10000,8000)
glm.fit = glm(default ~ income + balance, data = Default, family = binomial, 
        subset = train)
#iii
glm.probs = predict(glm.fit, Default[-train, ], type = "response")
glm.pred = rep("No", 2000)
glm.pred[glm.probs > 0.5] = "Yes"
#iv
mean(glm.pred != Default[-train, ]$default)
set.seed(45)
train=sample(10000,8000)
glm.fit = glm(default ~ income + balance, data = Default, family = binomial, 
        subset = train)
#iii
glm.probs = predict(glm.fit, Default[-train, ], type = "response")
glm.pred = rep("No", 2000)
glm.pred[glm.probs > 0.5] = "Yes"
#iv
mean(glm.pred != Default[-train, ]$default)
```

**c. When we set seed equals 20, and I splited the data into 80% training data and 20% validation data. The validation set error I got is 0.0275. Then I set the seed equals 40, the validation set error is 0.0265. Then I tried setting the seed = 45, I got test error rate is 0.031. Overall, my average test error rate is 0.0275**



```{r, echo=FALSE, eval=FALSE, warning=FALSE}
glm.fit = glm(default ~ income + balance + student, data = Default, family = binomial, 
    subset = train)
glm.pred = rep("No", 2000)
glm.probs = predict(glm.fit, Default[-train, ], type = "response")
glm.pred[glm.probs > 0.5] = "Yes"
mean(glm.pred != Default[-train, ]$default)
```
**d. after adding student dummy variable into the logistic logistic, , the test error rate is 0.0265.I don't think there's a reduction in the test error rate**
